Are environmental and geographic effective surrogates for genetic variation in conservation planning?

### 2015-12-24 article/article.tex
+ updated analysis to use equi-distant crs for attribute space + updated methods section in ms + attempting to set the supp info to be correct

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\ErrorTok}[1]{\textbf{{#1}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Are environmental and geographic effective surrogates for genetic variation in conservation planning?},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\setlength{\droptitle}{-2em}
  \title{Are environmental and geographic effective surrogates for genetic
variation in conservation planning?}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Jeffrey O. Hanson$^1$, Jonathan R. Rhodes$^2$, Cynthia Riginos$^2$, Hugh
P. Possingham$^1$, Richard A. Fuller$^1$\\$^1$School of Biological
Sciences, The University of Queensland, Brisbane, QLD,
Australia\\$^2$School of Geography, Planning and Environmental
Management, The University of Queensland, Brisbane, QLD,
Australia\\Correspondance should be addressed to
\href{mailto:jeffrey.hanson@uqconnect.edu.au}{jeffrey.hanson@uqconnect.edu.au}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{13 December 2015}

@@

{
\hypersetup{linkcolor=black}
\setcounter{tocdepth}{5}
\tableofcontents
}
\subsection{Introduction}\label{introduction}

@@

To address the aims of this study, we utilized species distribution and
genomic data collected by the IntraBioDiv project (Figure S1; Meirmans
\emph{et al.} 2011). As part of this project, data for 27 alpine plant
species were collected across the European Alps using a regular grid
(22.3 km $\times$ 25 km; see Gugerli \emph{et al.} 2008 for
methodological details). In every second cell, plant samples were
collected from three individiduals for each species present inside the
cell. Samples were genotyped using amplified fragment length
polymorphisms (AFLP; Vos \emph{et al.} 1995). Matrices denoting the
presence/absence of polymorphisms at loci were consutrcted independently
for each species. This dataset was well suited for the purposes of this
study, because it provides spatially explicit genomic data for a
multitude of species. Additionally, the study area spans across
broad-scale environmental gradients--ranging from lowlands to snow-caped
peaks--that have been found to correlate with genetic variation for some
of these species {[}{]}.

@@

We explored the effectiveness of environmental and geographic
surrogates. To describe variation in the location of each grid, we
projected the grids to an equal-area coordinate system (ESRI:102014) and
determined the centroid of each cell. To describe the climatic variation
among each cell, we obtained twenty-one bioclimatic variables (Hijmans
\emph{et al.} 2005). These layers were clipped to the extent of the grid
and subject to a principle components analysis (PCA; Table S1). The
first two principle components (PCs) cumulatively explained 97.2\% of
the variation and were used to generate two new layers. The average
value of each PC layer in each grid was used to characterise the
climatic conditions in the grid cell (Figure S2).

@@

To investigate the effectiveness of the surrogates for adaptive and
neutral genetic variation, we first identifed which of the sampled loci
for each species for each species were under selection. We used an
outlier locus detection method (evaluated in P{é}rez-Figueroa \emph{et
al.} 2010) to avoid circularity issues. The basic premise underpinning
this method is that neutral loci are expected to have a specific level
of variation among populations ($F_{st}$), and loci that deviate from
this expectation are under selection. Previously, Bothwell \emph{et al.}
(2013) applied such detection methods to one of the species
(\emph{Getiana nivalis}) in this dataset. Here, we applied their methods
to each of the twenty-seven species in the dataset.

Breifly, we grouped individuals into genetic lineages (Figure S2). The
purpose of this step was to avoid confounding variation between
populations with due to genetic history with variation attributed to
selection pressures. We used the Bayesian clustering method implemented
in Structure (version 2.3.4) assuming admixture and an independent
alleles model. For each species, we identified the most plausible number
of populations (K = 1--10; 4 runs for each K; model with lowest mean
posterior negative log likelihood; Figure S3), and estimated the
probability that each individual belonged to each population (10
burn-in; 10 iterations). Individuals with $\geq 0.75$ probability of
belonging to a single population were assigned accordingly (Figure S4),
and used for subseqent detection methods.

We used Bayescan (version 2.1; Foll and Gaggiotti 2008) to identify the
sampled loci under selection for each species (Table S2). For each
species, Bayescan was run using the population memberships identified
using Structure (1:1 prior odds, 3 pilot runs, and 10 iterations thinned
by 1 iterations with a 40 burn-in). Following guidelines in the Bayescan
manual, we omitted loci where the global frequency of the minor allele
was $\geq$ 0.05 to avoid false-positives. To ensure convergence, we ran
2 replicates per species using a false discovery rate (FDR) $\leq 0.5$.

After classifying the loci as adaptive or neutral for each species, we
mapped the main gradients of adaptive and/or neutral genetic variation
for each species (Figures S4--S29). For each species, we used Gower
distances to express the difference in adaptive and/or neutral
polymorphisms between individuals (using the cluster R package; Maechler
\emph{et al.} 2015). These distances were subject to a non metric
multi-dimensional scaling analysis (implemented in the vegan R package
using K=2 and 2 random starts; Table S3; Oksanen \emph{et al.} 2015).
The ordinated variables were then associated with the grid cells were
each species was sampled.

\subsubsection{Prioritisations}\label{prioritisations}

@@

\subsubsection{Single species
prioritisations}\label{single-species-prioritisations}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# prepare data for plotting}
\NormalTok{single.spp.PDF <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}
    \DataTypeTok{Prioritisation=}\KeywordTok{unique}\NormalTok{(single.spp.SDF$Prioritisation),}
    \DataTypeTok{Metric=}\KeywordTok{unique}\NormalTok{(single.spp.SDF$Metric))}
\NormalTok{single.spp.PDF <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(single.spp.PDF,}
    \KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{predict}\NormalTok{(single.spp.GLM, single.spp.PDF,}
        \DataTypeTok{type=}\StringTok{'response'}\NormalTok{, }\DataTypeTok{se.fit=}\OtherTok{TRUE}\NormalTok{))) %>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{lower=}\NormalTok{fit-se.fit, }\DataTypeTok{upper=}\NormalTok{fit+se.fit,}
        \DataTypeTok{letters=}\KeywordTok{toupper}\NormalTok{(}\KeywordTok{cld}\NormalTok{(single.spp.MCP)$mcletters$Letters),}
        \DataTypeTok{letter_pos=}\NormalTok{upper}\FloatTok{+0.05}\NormalTok{)}
\CommentTok{# make plot}
\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{Metric,}\DataTypeTok{y=}\NormalTok{fit,}\DataTypeTok{fill=}\NormalTok{Prioritisation),}
    \DataTypeTok{data=}\NormalTok{single.spp.PDF) +}
\StringTok{    }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{position=}\KeywordTok{position_dodge}\NormalTok{(}\FloatTok{0.9}\NormalTok{),}
        \DataTypeTok{stat=}\StringTok{'identity'}\NormalTok{) +}
\StringTok{    }\KeywordTok{geom_errorbar}\NormalTok{(}
        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin=}\NormalTok{lower,}\DataTypeTok{ymax=}\NormalTok{upper),}
        \DataTypeTok{position=}\KeywordTok{position_dodge}\NormalTok{(}\FloatTok{0.9}\NormalTok{), }\DataTypeTok{width=}\FloatTok{0.6}\NormalTok{) +}
\StringTok{    }\KeywordTok{geom_text}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{Metric, }\DataTypeTok{y=}\NormalTok{letter_pos,}
        \DataTypeTok{label=}\NormalTok{letters), }\DataTypeTok{position=}\KeywordTok{position_dodge}\NormalTok{(}\FloatTok{0.9}\NormalTok{)) +}
\StringTok{    }\KeywordTok{scale_fill_manual}\NormalTok{(}\DataTypeTok{name=}\StringTok{'Prioritisation'}\NormalTok{,}
        \DataTypeTok{values=}\KeywordTok{c}\NormalTok{(}\StringTok{'grey80'}\NormalTok{,}\StringTok{'grey50'}\NormalTok{,}\StringTok{'grey20'}\NormalTok{)) +}
\StringTok{    }\KeywordTok{ylab}\NormalTok{(}\StringTok{'Proportion genetic}\CharTok{\textbackslash{}n}\StringTok{variation secured (%)'}\NormalTok{) +}
\StringTok{    }\KeywordTok{xlab}\NormalTok{(}\StringTok{''}\NormalTok{) +}
\StringTok{    }\KeywordTok{theme_classic}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## ymax not defined: adjusting position using y instead
\end{verbatim}

\begin{figure}[htbp]
\centering
\includegraphics{article_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Summary of single species prioritisations. Single species
prioritisations were generated using amount-based targets, amount-based
and surrogate-based targets, and amount-based and genetic-based targets
for each species. Data shows the performance of prioritisations
generated using these three sets of targets. Bars denote means and
standard errors.}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# download basemap}
\KeywordTok{data}\NormalTok{(countriesHigh)}
\NormalTok{countries.FPLY <-}\StringTok{ }\NormalTok{countriesHigh[}
    \NormalTok{countriesHigh$ADMIN %in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}
        \StringTok{'Italy'}\NormalTok{, }\StringTok{'Switzerland'}\NormalTok{, }\StringTok{'France'}\NormalTok{, }\StringTok{'Austria'}\NormalTok{,}
        \StringTok{'Germany'}\NormalTok{, }\StringTok{'Slovenia'}\NormalTok{, }\StringTok{'Croatia'}\NormalTok{, }\StringTok{'Hungary'}\NormalTok{,}
        \StringTok{'Monaco'}\NormalTok{, }\StringTok{'Germany'}
    \NormalTok{)}
\NormalTok{,] %>%}\StringTok{ }\NormalTok{spFortify}
\CommentTok{# prepare data for plotting}
\NormalTok{multi.spp.grid.FPLY <-}\StringTok{ }\NormalTok{grid.PLY}
\NormalTok{for (i in }\KeywordTok{seq_along}\NormalTok{(multi.spp.prioritisations))}
    \NormalTok{multi.spp.grid.FPLY@data[[}\KeywordTok{paste0}\NormalTok{(}\StringTok{'v'}\NormalTok{,i)]] <-}\StringTok{ }\KeywordTok{selections}\NormalTok{(multi.spp.prioritisations[[i]])}
\NormalTok{multi.spp.grid.FPLY <-}\StringTok{ }\KeywordTok{spFortify}\NormalTok{(multi.spp.grid.FPLY)}
\CommentTok{# make maps}
\KeywordTok{do.call}\NormalTok{(}
    \NormalTok{grid.arrange,}
    \KeywordTok{append}\NormalTok{(}
        \KeywordTok{llply}\NormalTok{(}
            \KeywordTok{seq_along}\NormalTok{(multi.spp.prioritisations),}
            \NormalTok{function(i) \{}
                \KeywordTok{ggplot}\NormalTok{() +}
\StringTok{                    }\KeywordTok{geom_polygon}\NormalTok{(}\DataTypeTok{data=}\NormalTok{countries.FPLY, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{long, }\DataTypeTok{y=}\NormalTok{lat, }\DataTypeTok{group=}\NormalTok{group),}
                        \DataTypeTok{fill=}\StringTok{'grey20'}\NormalTok{, }\DataTypeTok{color=}\StringTok{'grey80'}\NormalTok{) +}
\StringTok{                    }\KeywordTok{geom_polygon}\NormalTok{(}\DataTypeTok{data=}\NormalTok{multi.spp.grid.FPLY, }\KeywordTok{aes_string}\NormalTok{(}\DataTypeTok{x=}\StringTok{'long'}\NormalTok{, }\DataTypeTok{y=}\StringTok{'lat'}\NormalTok{, }
                        \DataTypeTok{group=}\StringTok{'group'}\NormalTok{, }\DataTypeTok{fill=}\KeywordTok{paste0}\NormalTok{(}\StringTok{'v'}\NormalTok{,i)),}
                        \DataTypeTok{alpha=}\FloatTok{0.8}\NormalTok{, }\DataTypeTok{color=}\StringTok{'grey10'}\NormalTok{) +}
\StringTok{                    }\KeywordTok{guides}\NormalTok{(}\DataTypeTok{fill=}\KeywordTok{guide_legend}\NormalTok{(}\DataTypeTok{title=}\StringTok{' '}\NormalTok{)) +}
\StringTok{                    }\KeywordTok{theme_classic}\NormalTok{() +}
\StringTok{                    }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{axis.ticks=}\KeywordTok{element_blank}\NormalTok{(), }\DataTypeTok{axis.text=}\KeywordTok{element_blank}\NormalTok{(),}
                        \DataTypeTok{plot.margin=}\KeywordTok{unit}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{0}\NormalTok{,}\DecValTok{0}\NormalTok{,}\DecValTok{0}\NormalTok{),}\StringTok{'cm'}\NormalTok{), }\DataTypeTok{axis.line=}\KeywordTok{element_blank}\NormalTok{(),}
                        \DataTypeTok{legend.position=}\StringTok{'none'}\NormalTok{) +}
\StringTok{                    }\KeywordTok{coord_cartesian}\NormalTok{(}
                        \DataTypeTok{xlim=}\KeywordTok{buffered.range}\NormalTok{(multi.spp.grid.FPLY$long, }\FloatTok{0.05}\NormalTok{),}
                        \DataTypeTok{ylim=}\KeywordTok{buffered.range}\NormalTok{(multi.spp.grid.FPLY$lat, }\FloatTok{0.05}\NormalTok{)}
                    \NormalTok{) +}
\StringTok{                    }\KeywordTok{xlab}\NormalTok{(}\StringTok{''}\NormalTok{) +}
\StringTok{                    }\KeywordTok{ylab}\NormalTok{(}\StringTok{''}\NormalTok{) +}
\StringTok{                    }\KeywordTok{annotate}\NormalTok{(}\StringTok{'text'}\NormalTok{,}
                        \DataTypeTok{x=}\KeywordTok{min}\NormalTok{(multi.spp.grid.FPLY$long)+}\KeywordTok{diff}\NormalTok{(}\KeywordTok{range}\NormalTok{(multi.spp.grid.FPLY$long)*}\FloatTok{0.1}\NormalTok{),}
                        \DataTypeTok{y=}\KeywordTok{min}\NormalTok{(multi.spp.grid.FPLY$lat)+}\KeywordTok{diff}\NormalTok{(}\KeywordTok{range}\NormalTok{(multi.spp.grid.FPLY$lat)*}\FloatTok{1.01}\NormalTok{),}
                        \DataTypeTok{label=}\NormalTok{letters[i], }\DataTypeTok{hjust=}\DecValTok{1}\NormalTok{, }\DataTypeTok{vjust=}\DecValTok{1}\NormalTok{, }\DataTypeTok{color=}\StringTok{'white'}\NormalTok{, }\DataTypeTok{size=}\DecValTok{8}\NormalTok{)}
            \NormalTok{\}}
        \NormalTok{),}
        \KeywordTok{list}\NormalTok{(}\DataTypeTok{nrow=}\DecValTok{1}\NormalTok{)}
    \NormalTok{)}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[htbp]
\centering
\includegraphics{article_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Multi-species prioritisations. Panel (a) shows the
prioritisation generated for using just amount-based targets. Panel (b)
shows the prioritisation generated using amount-based and surrogate
based targets. Panel (c) shows the prioritisation generated using
amount-based and genetic-based targets}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# prepare data for plotting}
\NormalTok{multi.spp.PDF <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(}
    \DataTypeTok{Prioritisation=}\KeywordTok{unique}\NormalTok{(multi.spp.SDF$Prioritisation),}
    \DataTypeTok{Metric=}\KeywordTok{unique}\NormalTok{(multi.spp.SDF$Metric))}
\NormalTok{multi.spp.PDF <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(multi.spp.PDF,}
    \KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{predict}\NormalTok{(multi.spp.GLM, multi.spp.PDF,}
        \DataTypeTok{type=}\StringTok{'response'}\NormalTok{, }\DataTypeTok{se.fit=}\OtherTok{TRUE}\NormalTok{))) %>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{lower=}\NormalTok{fit-se.fit, }\DataTypeTok{upper=}\NormalTok{fit+se.fit,}
        \DataTypeTok{letters=}\KeywordTok{toupper}\NormalTok{(}\KeywordTok{cld}\NormalTok{(multi.spp.MCP)$mcletters$Letters),}
        \DataTypeTok{letter_pos=}\NormalTok{upper}\FloatTok{+0.05}\NormalTok{)}
\CommentTok{# make plot}
\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{Metric,}\DataTypeTok{y=}\NormalTok{fit,}\DataTypeTok{fill=}\NormalTok{Prioritisation),}
    \DataTypeTok{data=}\NormalTok{multi.spp.PDF) +}
\StringTok{    }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{position=}\KeywordTok{position_dodge}\NormalTok{(}\FloatTok{0.9}\NormalTok{),}
        \DataTypeTok{stat=}\StringTok{'identity'}\NormalTok{) +}
\StringTok{    }\KeywordTok{geom_errorbar}\NormalTok{(}
        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin=}\NormalTok{lower,}\DataTypeTok{ymax=}\NormalTok{upper),}
        \DataTypeTok{position=}\KeywordTok{position_dodge}\NormalTok{(}\FloatTok{0.9}\NormalTok{), }\DataTypeTok{width=}\FloatTok{0.6}\NormalTok{) +}
\StringTok{    }\KeywordTok{geom_text}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{Metric, }\DataTypeTok{y=}\NormalTok{letter_pos,}
        \DataTypeTok{label=}\NormalTok{letters), }\DataTypeTok{position=}\KeywordTok{position_dodge}\NormalTok{(}\FloatTok{0.9}\NormalTok{)) +}
\StringTok{    }\KeywordTok{scale_fill_manual}\NormalTok{(}\DataTypeTok{name=}\StringTok{'Prioritisation'}\NormalTok{,}
        \DataTypeTok{values=}\KeywordTok{c}\NormalTok{(}\StringTok{'grey80'}\NormalTok{,}\StringTok{'grey50'}\NormalTok{,}\StringTok{'grey20'}\NormalTok{)) +}
\StringTok{    }\KeywordTok{ylab}\NormalTok{(}\StringTok{'Proportion genetic}\CharTok{\textbackslash{}n}\StringTok{variation secured (%)'}\NormalTok{) +}
\StringTok{    }\KeywordTok{xlab}\NormalTok{(}\StringTok{''}\NormalTok{) +}
\StringTok{    }\KeywordTok{theme_classic}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## ymax not defined: adjusting position using y instead
\end{verbatim}

\begin{figure}[htbp]
\centering
\includegraphics{article_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Summary of multi-species prioritisations. Three prioritisations
were generated using amount-based targets, amount-based and
surrogate-based targets, and amount-based and genetic-based targets for
each species. Data shows the performance of these prioritisations based
on how much genetic variation they explain. Bars denote means and
standard errors.}
\end{figure}

@@

\subsection{Tables}\label{tables}

\subsection{Supporting Information}\label{supporting-information}

\subsubsection{Figure S1: Species
distributions}\label{figure-s1-species-distributions}

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Are environmental and geographic effective surrogates for genetic variation in conservation planning?},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\setlength{\droptitle}{-2em}
  \title{Are environmental and geographic effective surrogates for genetic
variation in conservation planning?}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Jeffrey O. Hanson$^1$, Jonathan R. Rhodes$^2$, Cynthia Riginos$^1$, Hugh
P. Possingham$^1$, Richard A. Fuller$^1$\\$^1$School of Biological
Sciences, The University of Queensland, Brisbane, QLD,
Australia\\$^2$School of Geography, Planning and Environmental
Management, The University of Queensland, Brisbane, QLD,
Australia\\Correspondance should be addressed to
\href{mailto:jeffrey.hanson@uqconnect.edu.au}{jeffrey.hanson@uqconnect.edu.au}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{24 December 2015}

@@

\subsection{Introduction}\label{introduction}

@@

To address the aims of the study, we utilized species distribution and
genomic data collected by the IntraBioDiv project (Figure S1; Meirmans
\emph{et al.} 2011; see Gugerli \emph{et al.} 2008 for methodological
details). This dataset was well suited for this study, because it
provides spatially explicit genomic data for a multitude of species
across a broad geographic area and over large environmental gradients.
As part of this project, data for 27 alpine plant species were collected
across the European Alps according to a grid (22.3 km $\times$ 25 km).
Briefly, in every second cell, plant samples were collected from three
individuals for each species present inside the cell. Samples were
genotyped using amplified fragment length polymorphisms (AFLP; Vos
\emph{et al.} 1995). Matrices denoting the presence/absence of
polymorphisms at loci were constructed independently for each species.
Thus for each second grid cell, for each of the species in the grid
cell, the dataset contains information describing the genomic variation
of individuals inside the grid cell. We used these grid cells as
planning units to develop prioritizations to investigate the
effectiveness of surrogates for the (AFLP) genetic variation.

@@

We explored the effectiveness of climatic and geographic surrogates. To
describe variation in the location of each grid cell, we projected the
grid into an equi-distant coordinate system (ESRI:102031) and used the
centroid of each cell. To describe the climatic variation among each
cell, we obtained twenty-one bioclimatic variables (approx. 1km
resolution; Hijmans \emph{et al.} 2005). These layers and the grid cells
were projected into an equal-area coordinate system (ESRI:102014). The
bioclimatic variables were clipped to the extent of the grid and subject
to a principle components analysis (PCA; Table S1). The first two
principle components (PCs) cumulatively explained 97.2\% of the
variation and were used to generate two new layers. We calculated the
average value for each PC layer in each grid cell, and used these values
to characterize the main themes of climatic variation among the grid
cells (Figure S2).

@@

To investigate the effectiveness of the surrogates for adaptive and
neutral genetic variation, we first identified which of the sampled loci
for each species were under selection. We used outlier locus detection
methods (evaluated in P{é}rez-Figueroa \emph{et al.} 2010) to avoid
circularity issues. The basic premise underpinning these analyses is
that neutral loci are expected to have a specific level of variation
among populations ($F_{st}$), and loci that deviate from this
expectation should be under selection. Thus loci can be identified as
being under selection without using environmental data. In an earlier
study, Bothwell \emph{et al.} (2013) applied such outlier detection
methods to one of the species in this dataset (\emph{Getiana nivalis}).
Here, we adopted a similar methodology and applied it to each of the 27
species in the dataset.

First, we grouped individuals into genetic lineages for each species
(Figure S2). The purpose of this step was to avoid confounding variation
between populations with due to genetic history with variation
attributed to selection pressures. We used the Bayesian clustering
method implemented in $\texttt{Structure}$ (version 2.3.4; Pritchard
\emph{et al.} 2000; Falush \emph{et al.} 2007) assuming admixture and an
independent alleles model. For each species, we identified the most
plausible number of populations (K = 1--2; 4 runs per K; 10 burn-in
iterations; 10 post-burn-in iterations) using the $\Delta$K method
(Figure S3; Evanno \emph{et al.} 2005). We aggregated the population
membership probabilities from replicate runs using $\texttt{CLUMPP}$
(version 1.1.2; large K greedy search method with 1000 random starts per
K per species; Figure S4; Jakobsson and Rosenberg 2007). Individuals
with a moderate probability of belonging to a single population
($\geq 0.75$) were assigned accordingly (Figure S5), and subject to
subsequent outlier locus detection methods.

We used $\texttt{Bayescan}$ (version 2.1; Foll and Gaggiotti 2008) to
identify loci under selection for each species (Table S2). For each
species, $\texttt{Bayescan}$ was run using the population memberships
identified in the previous analysis (1:1 prior odds; 3 pilot runs; 40
burn-in iterations; 10 post-burn-in iterations thinned by 1 iterations).
Following guidelines in the $\texttt{Bayescan}$ manual, we omitted loci
where the global frequency of the minor allele was $\geq 0.05$ to avoid
false-positives. To ensure convergence, we ran 2 replicates per species
using a suitable false discovery rate (FDR; $\leq 0.8$; Benjamini and
Hochberg 1995).

After classifying loci as adaptive or neutral, we mapped the main
gradients of the adaptive (if present) and neutral genetic variation for
each species (Figures S4--S29). Note that while individuals not assigned
to populations were omitted from the $\texttt{Bayescan}$ analysis, here
we used all the individuals. For each species, for each type of genetic
variation present, we used Gower distances (Gower 1971) to express the
genomic differences between individuals (using the cluster R package to
accommodate sparsity; Maechler \emph{et al.} 2015). These distances were
subject to a non metric multi-dimensional scaling analysis (implemented
in the vegan R package using K=2 and 2 random starts; Table S3; Oksanen
\emph{et al.} 2015). The average of the ordinated values associated with
individuals in each grid cell we used to characterize the genomic
variation in the grid cell.

\subsubsection{Prioritizations}\label{prioritizations}

We used the unreliable representative and adequate prioritization (URAP)
formulation of the reserve selection problem (Hanson \emph{et al.}
2016). We treated the genomic and surrogate variables as distinct
attribute spaces. We set the demand points for each species and its
attribute space using the values associated with the planning units.
First, we generated a set of single species prioritizations. For each
species, we generated a prioritization using a 20\% amount-based target,
a prioritization using a 20\% amount-based target and 90\% space-based
targets for the surrogate variation, and a prioritization using a 20\%
amount-based target and 90\% space-based targets for the genomic
variation. Next, we generated three multi-species prioritizations using
the same sets of targets used in the single species prioritizations.
Finally, to understand the relationship between the surrogate-based and
genomic-based targets, we generated a suite of prioritizations using
increasing space-based targets between 1\% and 100\% in increments of
49.5\%. For each prioritization we calculated the proportion of the
adaptive (if present) and neutral genetic variation that it secured. We
solved the reserve selection problems to within 90\% of optimality using
the $\texttt{rapr}$ R package (Hanson \emph{et al.} 2016) and
$\texttt{Gurobi}$ (Gurobi Optimization 2015).

@@

\subsubsection{Single species
prioritizations}\label{single-species-prioritizations}

@@

@@

Benjamini, Y., Hochberg, Y. (1995) Controlling the false discovery rate:
a practical and powerful approach to multiple testing. \emph{Journal of
the Royal Statistical Society. Series B (Methodological)}. \textbf{57},
289--300.
